Evolutionary demography and the maintenance of sexually antagonistic polymorphism in outcrossers and simultaneous hermaphrodites

### 2020-12-01 doc/SA-Hermaphrodites-wDemography.tex
Minor edits; fig changes
Not much.  Update files for work at office.

% Definitions
\def\mathbi#1{\textbf{\em #1}}
\def\mbf#1{\mathbf{#1}}
\def\mbb#1{\mathbb{#1}}
\def\mcal#1{\mathcal{#1}}
\newcommand{\bo}[1]{{\bf #1}}
\newcommand{\tr}{{\mbox{\tiny \sf T}}}
\newcommand{\bm}[1]{\mbox{\boldmath $#1$}}

 \def\linenumberfont{\normalfont\scriptsize}
%===========================================
% Basic info from Journal

@@

%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Demographic rate estimates for {\itshape M. guttatus}} \label{sec:MguttMethods}

To illustrate the use of our model with empirical data, and see whether demographic rates observed in natural populations are likely to support balanced SA polymorphisms, we used publicly available demographic and fitness data for natural populations of the hermaphroditic flowering plant {\itshape Mimulus guttatus} ({\itshape Erythranthe guttata}). {\itshape M.~guttatus}

>>>>

% Definitions
\def\mathbi#1{\textbf{\em #1}}
\def\mbf#1{\mathbf{#1}}
\def\mbb#1{\mathbb{#1}}
\def\mcal#1{\mathcal{#1}}
\newcommand{\bo}[1]{{\bf #1}}
\newcommand{\tr}{{\mbox{\tiny \sf T}}}
\newcommand{\bm}[1]{\mbox{\boldmath $#1$}}
\DeclareRobustCommand{\firstsecond}[2]{#2}
 \def\linenumberfont{\normalfont\scriptsize}
%===========================================
% Basic info from Journal

@@

%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Demographic and fitness data for {\itshape M. guttatus}} \label{sec:MguttMethods}

As an illustrative example of whether demographic rates observed in natural populations appear likely to support balanced SA polymorphisms, we parameterized our model using empirically estimated demographic rates and fitness data for natural populations of the partially-selfing hermaphroditic flowering plant {\itshape Mimulus guttatus} (Scrophulariaceae; now known as {\itshape Erythranthe guttata}). {\itshape M.~guttatus} is a well established study system for ecological and genomic studies because it shows high genetic diversity and significant variation in numerous ecologically relevant traits \citep{WuWillis2008}. In particular, there is well-documented variation in population selfing rates, and the severity of inbreeding depression has been estimated at multiple life-history stages for this species \citep[e.g.,][]{RitlandGanders1987, Ritland1990, Willis1993, Willis1999a, Willis1999b}. Moreover, detailed demographic studies have been conducted on multiple populations of {\itshape M.~guttatus}, with demographic matrix data made publicly available on the demographic database COMPADRE \citep{CompadreDB2020}. Below, we briefly outline how we parameterized our model using the available data; full details are provided in \hl{Appendix B.x}.
